Verifying Cache Coherence Protocols for an Infinite Family of Cache Hierarchies

### 2014-02-06 paper/Conclusion.tex
Conclusions added back and changed.

@@

>>>>

In this paper, we provided a formal definition of cache coherence via the store
atomicity property and provided a concrete hierarchy-parametric directory-based
MSI protocol whose correct we formally checked via a Coq-based proof. To our
knowledge this is the first instance of a formal proof of a protocol parametric
over the memory hierarchy.

Our protocol is described in a style amenable to mechanical transliteration to a
Bluespec SystemVerilog hardware description allowing us to provide high-quality
verified cache coherence engine. As the protocol and associated proof are robust
to many microarchitecture-oriented changes (\eg{} arbitrary hierarchy and
arbitrary cache size, associativity, and replacement policy choices in each
node), we should be able to produce a performant formally verified hardware
cache coherence system.

Moving this work towards generating a fully verified MSI implementation requires
a number of small steps. First, the simple transliteration of descriptions
between Bluespec and Coq, must be done in a mechanical way. Second, the
compilation of Bluespec to hardware is unverified; to fully trust the
implementation the Bluespec compiler must be verified. Some initial work on this
has already been done~\cite{TDBLP:conf/cav/BraibantC13}. Finally, we must extend
our notion of correctness to apply to the hardware substrate and not just the
level of atomic transactions. Most notably, this requires the some guarantee of
liveness and fairness in handling of messages in the final design. We have
initial Coq-based proofs that with finite buffers a local fairness in
transaction our protocol will have this property, but more work is needed to
fully resolve this venture.

@@

%%  LocalWords:  associativity atomicity
